---
title: "climex dataset"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{climex dataset}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

climex provides the daily climate data for each municipality in Mexico, downloaded from the [NASA Prediction Of Worldwide Energy Resources (POWER)](https://power.larc.nasa.gov) using the Python package [climex](https://github.com/fdzul/climex). climex uses the [Data Requests API](https://power.larc.nasa.gov/docs/tutorials/service-data-request/api/). The time series covers the period from January 1, 2020, to September 30, 2025. The 2025 dataset is updated weekly on Tuesday afternoons.


## Load the ewarsmx package
```{r setup}
library(ewarsmx)
```


## load the climex dataset 

```{r load_climex}
data("climex",package ="ewarsmx")
```

## explore the dataset

head and tail
```{r head}
head(climex)
```

```{r tail}
head(climex)
```

```{r}
dplyr::glimpse(climex)
```



```{r}
gtExtras::gt_plt_summary(climex)
```

```{r}
skimr::skim(climex)
```

